---
title: "Earthquakes in Fiji"
author: "Ivan Arambula"
date: "3/7/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Motivation

I found very interesting to experiment in how to display maps with data.

This Application was develop using Shiny in combination with Leaflet, the inspiration was based on an example of the maps using a dataset called quakes.

For more examples visit: <https://shiny.rstudio.com>.

There are multiple ways of how to use and enhance your R functionality with Shiny.

## UI code

One key piece was to use stylesheets (css)

```{r, echo=TRUE,eval=FALSE}
shinyUI(bootstrapPage(
    tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
    leafletOutput("map", width = "100%", height = "100%"),
    absolutePanel(id = "controls", 
                  style="border: 1px solid rgba(0, 0, 255, 0.09);
                         background: rgba(0, 0, 255, 0.09);",
                  div(style="padding:20px",h3("Earthquakes in Fiji"),
                      h6("by Magnitude (drag me)"),
                      sliderInput("range", "", min(quakes$mag), 
                                  max(quakes$mag),
                                  value = range(quakes$mag), step = 0.1
                      ),
                      div(style="overflow-y:scroll;height:220px",
                      tableOutput('table'))
                  ))))
```

## Details of quake dataset

There are two clear planes of seismic activity. One is a major plate junction; the other is the Tonga trench off New Zealand. These data constitute a subsample from a larger dataset of containing 5000 observations.

The application is running on <https://lengoman.shinyapps.io/EarthquakeInFiji/>.

And the source code can be found on github <https://github.com/lengoman/EarthquakesInFiji>.

## Thank you

I appreciate your time!
